Does a fully convective star need a special corona to produce a polar flare?

### 2023-08-08 src/tex/ms.tex
[showyourwork] overleaf sync

\subsection{X-ray luminosity}
\label{sec:discussion:xraylum}
Similar to its temperature make-up, while TIC~277's coronal luminosity relative to bolometric luminosity of $L_X/L_{\rm bol}=$\LXLbol is somewhat lower than the $L_X/L_{\rm bol}\sim 10^{-3}$ average in the saturated regime~\citep{wright2018stellar}, it is not an outlier to other M dwarfs in this activity regime.

In the Hyades and Praesepe, \citet{nunez2022factory} cover both fully convective and rapidly rotating M dwarfs, and find a downward trend in $L_X/L_{\rm bol}$ with decreasing rotation period for M3.5-M7 dwarfs, tentatively pointing toward a supersaturation of the corona at fast rotation speeds, as has been conjectured before~\citep{jeffries2011investigating,ramsay2020tess}.   \citet{jeffries2011investigating} suggest that the cause for supersaturation is centrifugal stripping of the corona, but \citet{reiners2022magnetism} show that if magnetic field increases, X-ray XXXX increases likewise with no sign of a break. They conclude that the trend is rather due to the underlying dynamo. If TIC~277 is indeed underluminous, these results suggest that its dynamo produces a weaker magnetic field than that of other saturated M dwarfs, which results in a slightly lower X-ray luminosity. However, since both the temperature structure and flaring activity of TIC~277 are in line with saturated activity, this conjecture currently lacks evidence from other activity indicators. Moreover, late M dwarfs are underrepresented in these studies.

>>>>

\subsection{X-ray luminosity}
\label{sec:discussion:xraylum}
Similar to its temperature make-up, while TIC~277's coronal luminosity relative to bolometric luminosity of $L_X/L_{\rm bol}=$\LXLbol is somewhat lower than the $L_X/L_{\rm bol}\sim 10^{-3}$ average in the saturated regime~\citep{wright2011stellaractivityrotation,wright2018stellar}, it is not an outlier to other M dwarfs in this activity regime.

In the Hyades and Praesepe, \citet{nunez2022factory} cover both fully convective and rapidly rotating M dwarfs, and find a downward trend in $L_X/L_{\rm bol}$ with decreasing rotation period for M3.5-M7 dwarfs, tentatively pointing toward a supersaturation of the corona at fast rotation speeds, as has been conjectured before~\citep{jeffries2011investigating,ramsay2020tess}.   \citet{jeffries2011investigating} suggest that the cause for supersaturation is centrifugal stripping of the corona, but \citet{reiners2022magnetism} show that if the averae surface magnetic field strength increases, $L_X/L_{\rm bol}$ increases likewise with no sign of a break, up to $10^{-3}$. They conclude that the trend is rather due to the underlying dynamo. If TIC~277 is indeed underluminous, these results suggest that its dynamo produces a weaker magnetic field than that of other saturated M dwarfs, which results in a slightly lower X-ray luminosity. However, since the flaring activity of TIC~277 is in line with saturated activity, this conjecture currently lacks evidence from other activity indicators~\citep[see][, for supersaturation in flaring activity in fully convective M dwarfs]{ramsay2020tess}. Moreover, late M dwarfs are underrepresented in these studies.
